---
title: "Meta-Analysis Notebook 2.0"
output:
  html_notebook: default
  html_document: default
  pdf_document: default
---

###This contains results for task variables, aggregated studies, and regressions
```{r echo=FALSE, include = FALSE}
library("compute.es")
library("metafor")
library("MAd")
library("meta")
header <- read.csv("~/R/PsyR/combined_meta2.csv",header = FALSE, skip = 1, nrows = 1, as.is = T, sep = ",", dec = ".")
data <- read.csv("~/R/PsYR/combined_meta2.csv", stringsAsFactors = FALSE, sep = ",", dec = ".")
colnames(data) <- header
data <- data[,-c(9:12)]
to.use <- which(data[,8] == 1)
data <- data[to.use,]
data$Type = toupper(data$Type)

#Data saved as characters, this converts them to numeric values
for (i in 9:18){ 
  data[,i] <- as.numeric(data[,i])
}

#Alter means based on polarity
meanCols = c(14,16)
data[,meanCols] = data[,meanCols] * data$Task_Value
```
This table lists the occurences of each Types
```{r}
#count occurences of each Type
for(i in 1:length(data$Type))
     {
  if (data$Type[i] == "EF-INHIBOTORY CONTROL" | data$Type[i] =="EF - INHIBITORY CONTROL")
    {
      data$Type[i] = "EF-INHIBITORY CONTROL"
  }
}
library(data.table)
data.table(data$Type)[,.N,by=data$Type]
```

```{r echo = FALSE, include = FALSE}
#function to be called on to remove task variable from coefficient name
#Parameters are length (number of characters to strip), v (vector of coefficient names)
taskTrim <- function(length, v)
  {
  for (i in 2:length(v)) #1 is the intercept, no need to alter this one
    {
    row.names(v)[i] = substring(row.names(v)[i], length+1)
    }
  return(v)
  }
```
Attention-Sustained has the most values, so I'll work with this one first. 
```{r echo = FALSE}
atsu_rows <- which(data$Type == "AT-SUSTAINED")
atsu <- data[atsu_rows,]

atsu.res <- mes(m.1 = Mean_Post_T, m.2 = Mean_Post_C, sd.1 = SD_Post_T, sd.2 = SD_Post_C, n.1 = nT, n.2 = nC,
           id = as.numeric(ID), data = atsu)
atsu.task.variable <- paste(atsu$Task, atsu$Variable, sep = " - ")
atsu.es <- cbind(atsu[c(1,2,3,5)],atsu.task.variable,atsu[c(8,9,10,11,12,18)], atsu.res[,c(13,14,15,16)])

atsu.res
atsu.es
```
Attention Sustained Task-Variable Coefficients
```{r echo = FALSE}

atsu.c <- cbind(atsu[c(1,2,3)],atsu.task.variable,atsu[9:21])

meta.atsu <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = atsu.task.variable, data = atsu.c, sm = "SMD",method.smd = "Hedges")
meta.atsu
```
Task-Variable Plots
```{r echo = FALSE}
funnel(meta.atsu)
forest(meta.atsu, leftcols=c("studlab"), fontsize = 6, plotwidth = "4cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Aggregated Results
```{r echo=FALSE}
study.atsu <- paste(atsu.c$Author, ", ", atsu.c$Year, sep="")
agg <- update(meta.atsu, byvar = study.atsu, bylab = "Study")
atsu.agg <- metabind(agg, pooled = "random")
atsu.agg
```

Regression
```{r echo = FALSE}
drop <- which(is.na(atsu.c$Num_Session) | is.na(atsu.c$Treat_Duration_Hour) | is.na(atsu.c$Home_Duration_Hour))
atsu2 <- atsu.c[-drop,]
meta.atsu2 <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = atsu.task.variable, data = atsu2, sm = "SMD",method.smd = "Hedges")
metareg(x = meta.atsu2, ~Num_Session + Treat_Duration_Hour + Home_Duration_Hour)
```

Aggregated Plots
```{r echo = FALSE}
funnel(atsu.agg)
forest(atsu.agg, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)

```
Attention-Selective
```{r echo = FALSE}
atse_rows <- which(data$Type == "AT-SELECTIVE")
atse <- data[atse_rows,]

atse.res <- mes(m.1 = Mean_Post_T, m.2 = Mean_Post_C, sd.1 = SD_Post_T, sd.2 = SD_Post_C, n.1 = nT, n.2 = nC,
           id = as.numeric(ID), data = atse)
atse.task.variable <- paste(atse$Task, atse$Variable, sep = " - ")
atse.es <- cbind(atse[c(1,2,3,5)],atse.task.variable,atse[c(8,9,10,11,12,18)], atse.res[,c(13,14,15,16)])

atse.res
atse.es
```
Task variable Coefficients
```{r echo = FALSE}

atse.c <- cbind(atse[c(1,2,3)],atse.task.variable,atse[9:21])

meta.atse <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = atse.task.variable, data = atse.c, sm = "SMD",method.smd = "Hedges")
meta.atse
```
Task-Variable Plots
```{r echo = FALSE}
funnel(meta.atse)
forest(meta.atse, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Aggregated Results
```{r echo =FALSE}
study.atse <- paste(atse.c$Author, ", ", atse.c$Year, sep="")
agg <- update(meta.atse, byvar = study.atse, bylab = "Study")
atse.agg <- metabind(agg, pooled = "random")
atse.agg
```

Regression
```{r echo = FALSE}
drop <- which(is.na(atse.c$Num_Session) | is.na(atse.c$Treat_Duration_Hour) | is.na(atse.c$Home_Duration_Hour))
atse2 <- atse.c[-drop,]
meta.atse2 <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = atse.task.variable, data = atse2, sm = "SMD",method.smd = "Hedges")
metareg(x = meta.atse2, ~Num_Session + Treat_Duration_Hour + Home_Duration_Hour)
```

Aggregated Plots
```{r echo = FALSE}
funnel(atse.agg)
forest(atse.agg, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Attention-Misc. Non-Distractability
```{r echo = FALSE}
atnd_rows <- which(data$Type == "AT-MISCELLANEOUS - NON-DISTRACTABILITY")
atnd <- data[atnd_rows,]

atnd.res <- mes(m.1 = Mean_Post_T, m.2 = Mean_Post_C, sd.1 = SD_Post_T, sd.2 = SD_Post_C, n.1 = nT, n.2 = nC,
           id = as.numeric(ID), data = atnd)
atnd.task.variable <- paste(atnd$Task, atnd$Variable, sep = " - ")
atnd.es <- cbind(atnd[c(1,2,3,5)],atnd.task.variable,atnd[c(8,9,10,11,12,18)], atnd.res[,c(13,14,15,16)])

atnd.res
atnd.es
```
Task Variable Coefficients
```{r echo = FALSE}

atnd.c <- cbind(atnd[c(1,2,3)],atnd.task.variable,atnd[9:21])

meta.atnd <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = atnd.task.variable, data = atnd.c, sm = "SMD",method.smd = "Hedges")
meta.atnd
```

Task-Variable Plots
```{r echo = FALSE}
funnel(meta.atnd)
forest(meta.atnd, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Aggregated Results
```{r echo = FALSE}
study.atnd <- paste(atnd.c$Author, ", ", atnd.c$Year, sep="")
agg <- update(meta.atnd, byvar = study.atnd, bylab = "Study")
atnd.agg <- metabind(agg, pooled = "random")
atnd.agg
```
Regression
```{r echo = FALSE}
drop <- which(is.na(atnd.c$Num_Session) | is.na(atnd.c$Treat_Duration_Hour) | is.na(atnd.c$Home_Duration_Hour))
atnd2 <- atnd.c[-drop,]
meta.atnd2 <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = atnd.task.variable, data = atnd2, sm = "SMD",method.smd = "Hedges")
metareg(x = meta.atnd2, ~Num_Session + Treat_Duration_Hour + Home_Duration_Hour)
```
Aggregated Plots
```{r echo = FALSE}
funnel(atnd.agg)
forest(atnd.agg, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```

Long-term Memory
```{r echo = FALSE}
lmdt_rows <- which(data$Type == "LM")
lmdt <- data[lmdt_rows,]

lmdt.res <- mes(m.1 = Mean_Post_T, m.2 = Mean_Post_C, sd.1 = SD_Post_T, sd.2 = SD_Post_C, n.1 = nT, n.2 = nC,
           id = as.numeric(ID), data = lmdt)
lmdt.task.variable <- paste(lmdt$Task, lmdt$Variable, sep = " - ")
lmdt.es <- cbind(lmdt[c(1,2,3,5)],lmdt.task.variable,lmdt[c(8,9,10,11,12,18)], lmdt.res[,c(13,14,15,16)])

lmdt.res
lmdt.es
```
Task Variable Coefficients
```{r echo = FALSE}

lmdt.c <- cbind(lmdt[c(1,2,3)],lmdt.task.variable,lmdt[9:21])

meta.lmdt <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = lmdt.task.variable, data = lmdt.c, sm = "SMD",method.smd = "Hedges")
meta.lmdt
```
Task-Variable Plots
```{r echo = FALSE}
funnel(meta.lmdt)
forest(meta.lmdt, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Aggregated Results
```{r echo=FALSE}
study.lmdt <- paste(lmdt.c$Author, ", ", lmdt.c$Year, sep="")
agg <- update(meta.lmdt, byvar = study.lmdt, bylab = "Study")
lmdt.agg <- metabind(agg, pooled = "random")
lmdt.agg
```
Regression
```{r echo = FALSE}
drop <- which(is.na(lmdt.c$Num_Session) | is.na(lmdt.c$Treat_Duration_Hour) | is.na(lmdt.c$Home_Duration_Hour))
lmdt2 <- lmdt.c[-drop,]
meta.lmdt2 <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = lmdt.task.variable, data = lmdt2, sm = "SMD",method.smd = "Hedges")
metareg(x = meta.lmdt2, ~Num_Session + Treat_Duration_Hour + Home_Duration_Hour)
```

Aggregated Plots
```{r echo = FALSE}
funnel(lmdt.agg)
forest(lmdt.agg, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)

```

Working Memory
```{r echo = FALSE}
wmdt_rows <- which(data$Type == "WM")
wmdt <- data[wmdt_rows,]

wmdt.res <- mes(m.1 = Mean_Post_T, m.2 = Mean_Post_C, sd.1 = SD_Post_T, sd.2 = SD_Post_C, n.1 = nT, n.2 = nC,
           id = as.numeric(ID), data = wmdt)
wmdt.task.variable <- paste(wmdt$Task, wmdt$Variable, sep = " - ")
wmdt.es <- cbind(wmdt[c(1,2,3,5)],wmdt.task.variable,wmdt[c(8,9,10,11,12,18)], wmdt.res[,c(13,14,15,16)])

wmdt.res
wmdt.es
```
Task Variable coefficients
```{r echo = FALSE}

wmdt.c <- cbind(wmdt[c(1,2,3)],wmdt.task.variable,wmdt[9:21])

meta.wmdt <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = wmdt.task.variable, data = wmdt.c, sm = "SMD",method.smd = "Hedges")
meta.wmdt
```
Task-Variable Plots
```{r echo = FALSE}
funnel(meta.wmdt)
forest(meta.wmdt, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Aggregate Results
```{r echo = FALSE}
study.wmdt <- paste(wmdt.c$Author, ", ", wmdt.c$Year, sep="")
agg <- update(meta.wmdt, byvar = study.wmdt, bylab = "Study")
wmdt.agg <- metabind(agg, pooled = "random")
wmdt.agg
```
Regression
```{r echo = FALSE}
drop <- which(is.na(wmdt.c$Num_Session) | is.na(wmdt.c$Treat_Duration_Hour) | is.na(wmdt.c$Home_Duration_Hour))
wmdt2 <- wmdt.c[-drop,]
meta.wmdt2 <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = wmdt.task.variable, data = wmdt2, sm = "SMD",method.smd = "Hedges")
metareg(x = meta.wmdt2, ~Num_Session + Treat_Duration_Hour + Home_Duration_Hour)
```

Aggregated Plots
```{r echo = FALSE}
funnel(wmdt.agg)
forest(wmdt.agg, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Executive Functioning and Working Memory
```{r echo = FALSE}
efwm_rows <- which(data$Type == "EF AND WM")
efwm <- data[efwm_rows,]

efwm.res <- mes(m.1 = Mean_Post_T, m.2 = Mean_Post_C, sd.1 = SD_Post_T, sd.2 = SD_Post_C, n.1 = nT, n.2 = nC,
           id = as.numeric(ID), data = efwm)
efwm.task.variable <- paste(efwm$Task, efwm$Variable, sep = " - ")
efwm.es <- cbind(efwm[c(1,2,3,5)],efwm.task.variable,efwm[c(8,9,10,11,12,18)], efwm.res[,c(13,14,15,16)])

efwm.res
efwm.es
```
Task Variable Coefficients
```{r echo = FALSE}

efwm.c <- cbind(efwm[c(1,2,3)],efwm.task.variable,efwm[9:21])

meta.efwm <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = efwm.task.variable, data = efwm.c, sm = "SMD",method.smd = "Hedges")
meta.efwm
```
Task-Variable Plots
```{r echo = FALSE}
funnel(meta.efwm)
forest(meta.efwm, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Aggregated Results
```{r echo = FALSE}
study.efwm <- paste(efwm.c$Author, ", ", efwm.c$Year, sep="")
agg <- update(meta.efwm, byvar = study.efwm, bylab = "Study")
efwm.agg <- metabind(agg, pooled = "random")
efwm.agg
```
Regression
```{r echo = FALSE}
drop <- which(is.na(efwm.c$Num_Session) | is.na(efwm.c$Treat_Duration_Hour) | is.na(efwm.c$Home_Duration_Hour))
efwm2 <- efwm.c[-drop,]
meta.efwm2 <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = efwm.task.variable, data = efwm2, sm = "SMD",method.smd = "Hedges")
metareg(x = meta.efwm2, ~Num_Session + Treat_Duration_Hour + Home_Duration_Hour)
```
Aggregated Plots
```{r echo = FALSE}
funnel(efwm.agg)
forest(efwm.agg, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)

```
Executive Functioning- Conflict Monitoring
```{r echo = FALSE}
efcm_rows <- which(data$Type == "EF-CONFLICT MONITORING")
efcm <- data[efcm_rows,]

efcm.res <- mes(m.1 = Mean_Post_T, m.2 = Mean_Post_C, sd.1 = SD_Post_T, sd.2 = SD_Post_C, n.1 = nT, n.2 = nC,
           id = as.numeric(ID), data = efcm)
efcm.task.variable <- paste(efcm$Task, efcm$Variable, sep = " - ")
efcm.es <- cbind(efcm[c(1,2,3,5)],efcm.task.variable,efcm[c(8,9,10,11,12,18)], efcm.res[,c(13,14,15,16)])

efcm.res
efcm.es
```
Task Variable Coefficients
```{r echo = FALSE}

efcm.c <- cbind(efcm[c(1,2,3)],efcm.task.variable,efcm[9:21])

meta.efcm <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = efcm.task.variable, data = efcm.c, sm = "SMD",method.smd = "Hedges")
meta.efcm
```
Task-Variable Plots
```{r echo = FALSE}
funnel(meta.atsu)
forest(meta.atsu, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Aggregated Results
```{r echo = FALSE}
study.efcm <- paste(efcm.c$Author, ", ", efcm.c$Year, sep="")
agg <- update(meta.efcm, byvar = study.efcm, bylab = "Study")
efcm.agg <- metabind(agg, pooled = "random")
efcm.agg
```

Regression
```{r echo = FALSE}
drop <- which(is.na(efcm.c$Num_Session) | is.na(efcm.c$Treat_Duration_Hour) | is.na(efcm.c$Home_Duration_Hour))
efcm2 <- efcm.c[-drop,]
meta.efcm2 <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = efcm.task.variable, data = efcm2, sm = "SMD",method.smd = "Hedges")
metareg(x = meta.efcm2, ~Num_Session + Treat_Duration_Hour + Home_Duration_Hour)
```
Aggregated Plots
```{r echo = FALSE}
funnel(efcm.agg)
forest(efcm.agg, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)

```
Executive Functioning-Decision Making
```{r echo = FALSE}
efdm_rows <- which(data$Type == "EF-DECISION MAKING")
efdm <- data[efdm_rows,]

efdm.res <- mes(m.1 = Mean_Post_T, m.2 = Mean_Post_C, sd.1 = SD_Post_T, sd.2 = SD_Post_C, n.1 = nT, n.2 = nC,
           id = as.numeric(ID), data = efdm)
efdm.task.variable <- paste(efdm$Task, efdm$Variable, sep = " - ")
efdm.es <- cbind(efdm[c(1,2,3,5)],efdm.task.variable,efdm[c(8,9,10,11,12,18)], efdm.res[,c(13,14,15,16)])

efdm.res
efdm.es
```
Task Variable Coefficients
```{r echo = FALSE}

efdm.c <- cbind(efdm[c(1,2,3)],efdm.task.variable,efdm[9:21])

meta.efdm <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = efdm.task.variable, data = efdm.c, sm = "SMD",method.smd = "Hedges")
meta.efdm
```
Task-Variable Plots
```{r echo = FALSE}
funnel(meta.efdm)
forest(meta.efdm, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Aggregated Results
```{r echo = FALSE}
study.efdm <- paste(efdm.c$Author, ", ", efdm.c$Year, sep="")
agg <- update(meta.efdm, byvar = study.efdm, bylab = "Study")
efdm.agg <- metabind(agg, pooled = "random")
efdm.agg
```
Regression
```{r echo = FALSE}
drop <- which(is.na(efdm.c$Num_Session) | is.na(efdm.c$Treat_Duration_Hour) | is.na(efdm.c$Home_Duration_Hour))
efdm2 <- efdm.c[-drop,]
meta.efdm2 <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = efdm.task.variable, data = efdm2, sm = "SMD",method.smd = "Hedges")
metareg(x = meta.efdm2, ~Num_Session + Treat_Duration_Hour + Home_Duration_Hour)
```
Aggregated Plots
```{r echo = FALSE}
funnel(efdm.agg)
forest(efdm.agg, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)

```
Executive Functioning- Planning
```{r echo = FALSE}
efpd_rows <- which(data$Type == "EF-PLANNING")
efpd <- data[efpd_rows,]

efpd.res <- mes(m.1 = Mean_Post_T, m.2 = Mean_Post_C, sd.1 = SD_Post_T, sd.2 = SD_Post_C, n.1 = nT, n.2 = nC,
           id = as.numeric(ID), data = efpd)
efpd.task.variable <- paste(efpd$Task, efpd$Variable, sep = " - ")
efpd.es <- cbind(efpd[c(1,2,3,5)],efpd.task.variable,efpd[c(8,9,10,11,12,18)], efpd.res[,c(13,14,15,16)])

efpd.res
efpd.es
```
Task Variable Coefficients
```{r echo = FALSE}
efpd.c <- cbind(efpd[c(1,2,3)],efpd.task.variable,efpd[9:21])

meta.efpd <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = efpd.task.variable, data = efpd.c, sm = "SMD",method.smd = "Hedges")
meta.efpd
```
Task-Variable Plots
```{r echo = FALSE}
funnel(meta.efpd)
forest(meta.efpd, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Aggregated Results
```{r echo = FALSE}
study.efpd <- paste(efpd.c$Author, ", ", efpd.c$Year, sep="")
agg <- update(meta.efpd, byvar = study.efpd, bylab = "Study")
efpd.agg <- metabind(agg, pooled = "random")
efpd.agg
```
Regression
```{r echo = FALSE}
drop <- which(is.na(efpd.c$Num_Session) | is.na(efpd.c$Treat_Duration_Hour) | is.na(efpd.c$Home_Duration_Hour))
efpd2 <- efpd.c[-drop,]
meta.efpd2 <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = efpd.task.variable, data = efpd2, sm = "SMD",method.smd = "Hedges")
metareg(x = meta.efpd2, ~Num_Session + Treat_Duration_Hour + Home_Duration_Hour)
```
Aggregated Plots
```{r echo = FALSE}
funnel(efpd.agg)
forest(efpd.agg, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Executive Functioning- Cognitive Flexibility
```{r echo = FALSE}
efcf_rows <- which(data$Type == "EF-COGNITIVE FLEXIBILITY")
efcf <- data[efcf_rows,]

efcf.res <- mes(m.1 = Mean_Post_T, m.2 = Mean_Post_C, sd.1 = SD_Post_T, sd.2 = SD_Post_C, n.1 = nT, n.2 = nC,
           id = as.numeric(ID), data = efcf)
efcf.task.variable <- paste(efcf$Task, efcf$Variable, sep = " - ")
efcf.es <- cbind(efcf[c(1,2,3,5)],efcf.task.variable,efcf[c(8,9,10,11,12,18)], efcf.res[,c(13,14,15,16)])

efcf.res
efcf.es
```
Task Variable Coefficients
```{r echo = FALSE}

efcf.c <- cbind(efcf[c(1,2,3)],efcf.task.variable,efcf[9:21])

meta.efcf <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = efcf.task.variable, data = efcf.c, sm = "SMD",method.smd = "Hedges")
meta.efcf
```
Task-Variable Plots
```{r echo = FALSE}
funnel(meta.efcf)
forest(meta.efcf, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Aggregated Results
```{r echo=FALSE}
study.efcf <- paste(efcf.c$Author, ", ", efcf.c$Year, sep="")
agg <- update(meta.efcf, byvar = study.efcf, bylab = "Study")
efcf.agg <- metabind(agg, pooled = "random")
efcf.agg
```
Regression
```{r echo = FALSE}
drop <- which(is.na(efcf.c$Num_Session) | is.na(efcf.c$Treat_Duration_Hour) | is.na(efcf.c$Home_Duration_Hour))
efcf2 <- efcf.c[-drop,]
meta.efcf2 <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = efcf.task.variable, data = efcf2, sm = "SMD",method.smd = "Hedges")
metareg(x = meta.efcf2, ~Num_Session + Treat_Duration_Hour + Home_Duration_Hour)
```
Aggregated Plots
```{r echo = FALSE}
funnel(efcf.agg)
forest(efcf.agg, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)

```
Executive Functioning- Inhibitory Control
```{r echo = FALSE}
efic_rows <- which(data$Type == "EF-INHIBITORY CONTROL")
efic <- data[efic_rows,]

efic.res <- mes(m.1 = Mean_Post_T, m.2 = Mean_Post_C, sd.1 = SD_Post_T, sd.2 = SD_Post_C, n.1 = nT, n.2 = nC,
           id = as.numeric(ID), data = efic)
efic.task.variable <- paste(efic$Task, efic$Variable, sep = " - ")
efic.es <- cbind(efic[c(1,2,3,5)],efic.task.variable,efic[c(8,9,10,11,12,18)], efic.res[,c(13,14,15,16)])

efic.res
efic.es
```
Task Variable Coefficients
```{r echo = FALSE}

efic.c <- cbind(efic[c(1,2,3)],efic.task.variable,efic[9:21])

meta.efic <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = efic.task.variable, data = efic.c, sm = "SMD",method.smd = "Hedges")
meta.efic
```
Task-Variable Plots
```{r echo = FALSE}
funnel(meta.efic)
forest(meta.efic, leftcols=c("studlab"), fontsize = 8, plotwidth = "5cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```
Aggregated Results
```{r echo = FALSE}
study.efic <- paste(efic.c$Author, ", ", efic.c$Year, sep="")
agg <- update(meta.efic, byvar = study.efic, bylab = "Study")
efic.agg <- metabind(agg, pooled = "random")
efic.agg
```

Regression
```{r echo = FALSE}
drop <- which(is.na(efic.c$Num_Session) | is.na(efic.c$Treat_Duration_Hour))
efic2 <- efic.c[-drop,]
meta.efic2 <- metacont(n.e = nT, mean.e = Mean_Post_T, sd.e = SD_Post_T, 
                    n.c = nC, mean.c = Mean_Post_C, sd.c = SD_Post_C,
                    studlab = efic.task.variable, data = efic2, sm = "SMD",method.smd = "Hedges")
metareg(x = meta.efic2, ~Num_Session + Treat_Duration_Hour + Home_Duration_Hour)
efic2
```
Aggregated Plots
```{r echo = FALSE}
funnel(efic.agg)
forest(efic.agg, leftcols=c("studlab"), fontsize = 10, plotwidth = "6cm", weight.study="random", squaresize =0, col.square = "black", label.right="Favors mindfullness-based", label.left = "Favors control", bylab = "Study",
       overall = TRUE)
```